Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Minor edits.

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

>>>>

\subsection{Packet length}

Protocols vary in their packet lengths;
a censor may block a circumvention protocol if its length distribution
is distinct enough.
Figure~\ref{fig:datalen}
compares the packet length distribution of both sample traffic traces in both directions.
In both cases, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
frequent packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.
